CAROUGE - the new metric for text summarization

### 2018-06-10 paper/paper.tex
Changed the title

\title{Automatic Summarization of Scientific Texts}

@@

\paragraph{Cleaning the text} We collected our data as PDF files and parsed them to extract the raw text. This produced a huge amount of uniterpretable UTF-8 characters from mathematical expressions. After removing those extra characters.

We wanted to remove everething that is not a known English word, but that would filter out words like "GAN", "backprop" etc. as most standard corpuses of words, such as nltk.corpus, don't include specialized scientific terminology. So we filtered the words using manually created rules based on features like word length and frequence of vowels. This leaves some noise behind, but it will not affect our models.

@@

\begin{enumerate}
\item assume that a good summary would be close to some \textit{ideal} summary manually created by humans
\item assume that the goodness of summary can be measured as the ammount of important information it contains (this assumption can be infered from the definition of text summarization).
\end{enumerate}

@@

ROUGE works well for extractive text summarization. But if we need to evaluate the generated summary which contains different words from the ones that occured in paper, the score will always be small because, even though the new words can be close to the expected ones, two summaries don't overlap in terms of word equality.

@@

The metric we propose is in fact a continuous version of ROUGE-N. Instead of testing the equality of n-grams in the compared summaries we use the continuous measure of semmantic distance between those n-grams.

@@

Rapid Automatic Keyword Extraction algorithm (RAKE)\cite{rose-10} is a keyword extraction algorithm which tries to determine key phrases in a body of text by analyzing the frequency of word appearance and its co-occurance with other words in the text. Its main advantages include time efficiency, operating on individual documents. It can be easily applied to new domains and multiple types of documents. RAKE is very sensitive to unclean data, as it relies on word frequency.

@@

We would like to express our gratitude to Anatolii Stehnii, Artem Chernodub, and Maryana Romanyshyn for helping us with their advices. Also, we are very grateful to Rostyslav Zatserkovnyi, Anton Tarasov, Ivan Ilnytskyi, Taras Panychok, and Bohdan Petryshak for providing their manually created summaries of some papers from our dataset.

>>>>

\title{CAROUGE - the new metric for text summarization}

@@

\paragraph{Cleaning the text} We collected our data as PDF files and parsed them to extract the raw text. This produced a huge amount of uninterpretable UTF-8 characters from mathematical expressions. After removing those extra characters.

We wanted to remove everything that is not a known English word, but that would filter out words like "GAN", "backprop" etc. as most standard corpora of words, such as nltk.corpus, don't include specialized scientific terminology. So we filtered the words using manually created rules based on features like word length and frequency of vowels. This leaves some noise behind, but it will not affect our models.

@@

\begin{enumerate}
\item assume that a good summary would be close to some \textit{ideal} summary manually created by humans
\item assume that the goodness of summary can be measured as the amount of important information it contains (this assumption can be inferred from the definition of text summarization).
\end{enumerate}

@@

ROUGE works well for extractive text summarization. But if we need to evaluate the generated summary which contains different words from the ones that occurred in paper, the score will always be small because, even though the new words can be close to the expected ones, two summaries don't overlap in terms of word equality.

@@

The metric we propose is in fact a continuous version of ROUGE-N. Instead of testing the equality of n-grams in the compared summaries we use the continuous measure of semantic distance between those n-grams.

@@

Rapid Automatic Keyword Extraction algorithm (RAKE)\cite{rose-10} is a keyword extraction algorithm which tries to determine key phrases in a body of text by analyzing the frequency of word appearance and its co-occurrance with other words in the text. Its main advantages include time efficiency, operating on individual documents. It can be easily applied to new domains and multiple types of documents. RAKE is very sensitive to unclean data, as it relies on word frequency.

@@

We would like to express our gratitude to Anatolii Stehnii, Artem Chernodub, and Maryana Romanyshyn for helping us with their valuable pieces of advice. Also, we are very grateful to Rostyslav Zatserkovnyi, Anton Tarasov, Ivan Ilnytskyi, Taras Panychok, and Bohdan Petryshak for providing their manually created summaries of some papers from our dataset.
